---
output: github_document
always_allow_html: yes
editor_options:
  markdown:
    wrap: sentence
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# otel

> OpenTelemetry API for R packages and projects

<!-- badges: start -->
![lifecycle](https://lifecycle.r-lib.org/articles/figures/lifecycle-experimental.svg) [![R-CMD-check](https://github.com/r-lib/otel/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-lib/otel/actions/workflows/R-CMD-check.yaml)
[![R-CMD-check](https://github.com/r-lib/otel/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-lib/otel/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/r-lib/otel/graph/badge.svg)](https://app.codecov.io/gh/r-lib/otel)
<!-- badges: end -->

```{r child = system.file(package = "otel", "dox", "intro.Rmd")}
```

```{r child = system.file(package = "otel", "dox", "features.Rmd")}
```

## Getting started

Set `otel_tracer_name` to the desired tracer name. (See `?otel_tracer_name`.)
Then add `otel::start_local_active_span()` calls to the functions you want
to trace:

```r
otel_tracer_name <- "<package-id>"
fn <- function(...) {
  spn <- otel::start_local_active_span("fn")
  ...
}
```

See [Getting Started](TODO) for details.

```{r child = system.file(package = "otel", "dox", "packages.Rmd")}
```

```{r child = system.file(package = "otel", "dox", "reference-docs.Rmd")}
```

```{r child = system.file(package = "otel", "dox", "status.Rmd")}
```

```{r child = system.file(package = "otel", "dox", "version-support.Rmd")}
```

## Installation

Install otel from CRAN:

``` r
# install.packages("pak")
pak::pak("otel")
```

You can install the development version of otel from
[GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("r-lib/otel")
```

```{r child = system.file(package = "otel", "dox", "repositories.Rmd")}
```

## License

MIT © Posit, PBC
